\documentclass{ximera}

\author{Anna Davis} \title{MTH 140 Quiz 12} 

\begin{document}

\begin{abstract}

\end{abstract}
\maketitle
 \textit{Soft Deadline: April 20, 2020}
\begin{problem}\label{prob:140quiz12prob1}
Suppose a student advocacy group is trying to determine whether there is a difference between the average textbook cost for college freshmen and college seniors.  The group surveys eight randomly selected freshmen and eleven seniors.  The results are listed below.  Perform hypothesis testing at 0.05 level of significance. (You may assume that textbook costs are approximately normally distributed.)

Freshmen: \$155, \$280, \$98, \$163, \$178, \$210, \$173, \$169

Seniors: \$145, \$180, \$197, \$238, \$215, \$110, \$153, \$116, \$203, \$54, \$105  

Summarize the information for college freshmen.
$$\overline{x}_f=\answer[tolerance=0.01]{178.25},\quad s_f=\answer[tolerance=0.01]{51.67},\quad n_f=\answer{8}$$

Summarize the information for college seniors.
$$\overline{x}_s=\answer[tolerance=0.01]{156},\quad s_s=\answer[tolerance=0.01]{56.14},\quad n_s=\answer{11}$$

Null Hypothesis:

$H_0:\quad \mu_f-\mu_s$ \wordChoice{\choice{$\leq0$}, \choice[correct]{$=0$}, \choice{$\geq 0$}}

Alternative Hypothesis:

$H_a:\quad \mu_f-\mu_s$ \wordChoice{\choice{$<0$}, \choice[correct]{$\neq 0$}, \choice{$>0$}}

Find the $t$-score
$$t=\answer[tolerance=0.01]{0.893}$$
Find degrees of freedom
$$\mbox{df}=\answer[tolerance=0.01]{15.95}$$
Find the $p$-value
\begin{center}  
\geogebra{emwxhga2}{800}{600}  
\end{center}
$$p=\answer[tolerance=0.001]{0.3852}$$
Decision:

\begin{multipleChoice} 
\choice{$p$-value is less than 0.05.  We reject the null hypothesis.}  
\choice{$p$-value is less than 0.05.  We do not reject the null hypothesis.} 
\choice{$p$-value is greater than 0.05.  We reject the null hypothesis.} 
\choice[correct]{$p$-value is greater than 0.05.  We do not reject the null hypothesis.}  
\end{multipleChoice}  

Conclusion:

\begin{multipleChoice} 
\choice{At the 0.05 level of significance, we have proved the null hypothesis.}  
\choice{At the 0.05 level of significance, there is not enough evidence to make any conclusions.} 
\choice{At the 0.05 level of significance, there is enough evidence to conclude that the mean textbook cost for freshmen is higher than the mean textbook cost for seniors.}  
\choice[correct]{At the 0.05 level of significance, there is not enough evidence to conclude that the mean textbook cost for freshmen is different from the mean textbook cost for seniors.} 
\end{multipleChoice} 
\end{problem}

\end{document} 