\documentclass{ximera}

\author{Anna Davis} \title{MTH 160 Homework 7} 

\begin{document}

\begin{abstract}

\end{abstract}
\maketitle
 \textit{Certificate due: 10/21/2020 at 11:59 p.m.}
 \section{Lecture 16}
 
  \begin{problem}\label{prob:160hom7prob1} 
Let $f(x)=-3^{-x}+1$.  Evaluate.
  \begin{enumerate}
\item
 $$f(-2)=\answer{-8}$$
\item (Enter exact answer; no decimal approximations)
$$f(3)=\answer{26/27}$$
  \end{enumerate}
\end{problem}  
   \begin{problem}\label{prob:160hom7prob2}
 Find the horizontal asymptote and the $y$-intercept for each function.
 \begin{enumerate}
     \item $f(x)=4(2^x)-10$
     
     Horizontal Asymptote: $y=\answer{-10}$
     
     $y$-intercept: $(0, \answer{-6})$
      \item $g(x)=3^{-x}+7$
     
     Horizontal Asymptote: $y=\answer{7}$
     
     $y$-intercept: $(0, \answer{8})$
     \item $h(x)=-2^{-x}$
     
     Horizontal Asymptote: $y=\answer{0}$
     
     $y$-intercept: $(0, \answer{-1})$
 \end{enumerate}
   \end{problem}

\begin{problem}\label{prob:160hom7prob3}
Fill out the table of values for $f(x)=3^x$.  Use exact values; no decimal approximations.
\begin{center}
\begin{tabular}{|c|c|}
 \hline
 &   \\
 $x$& $f(x)$ \\
 &  \\
  \hline
  &  \\
 $0$ & $\answer{1}$ \\
  & \\
 \hline
  & \\
 $1$ & $\answer{3}$ \\
  & \\
 \hline
  & \\
  $2$ & $\answer{9}$  \\
  & \\
 \hline
 & \\
  $-1$ & $\answer{1/3}$  \\
  & \\
 \hline
 & \\
  $-2$ & $\answer{1/9}$  \\
  & \\
 \hline
 & \\
  $-3$ & $\answer{1/27}$  \\
  & \\
 \hline
 \end{tabular}
\end{center}    
\end{problem}

\section{Lecture 17}
 
  \begin{problem}\label{prob:160hom7prob4} 
  Suppose $\$5000$ is deposited into a savings account that pays $0.5\%$ annual interest rate.  
  Summarize the information:
  $$P=\answer{5000},\quad r=\answer{0.005}$$
  Find the amount of money in the account at the end of 2 years if the interest is compounded in each of the ways listed in the table.  Round your answers to two decimal places.
  \begin{center}
\begin{tabular}{|c|c|c|}
 \hline
 &&   \\
 Interest is compounded... & $n$ & Amount after 2 years \\
 &&  \\
  \hline
  &&  \\
 Quarterly & $\answer{4}$ & $\answer{5050.22}$ \\
  && \\
 \hline
  &&  \\
 Monthly & $\answer{12}$ & $\answer{5050.24}$ \\
  && \\
 \hline
  &&  \\
 Daily & $\answer{365}$ & $\answer{5050.25}$ \\
  && \\
 \hline
 \end{tabular}
\end{center}    
  \end{problem}
  
  \begin{problem}\label{prob:160hom7prob5} 
  Suppose $\$2000$ is deposited into a savings account that pays $0.6\%$ annual interest rate compounded quarterly.  Sketch the graph to determine how long it will take for the amount to grow to  $\$2100$.  Use Desmos and round your answers to three decimal places.
  
  \begin{center}  
\desmos{vnpejaj7ps}{800}{600}  
\end{center}

It will take $\answer{8.138}$ years for the amount in the account to grow to $\$2100$.  
  \end{problem}
  
  \begin{problem}\label{prob:160hom7prob6}
  Suppose $\$3460$ is deposited into an account that pays $0.35\%$ annual interest rate compounded continuously.  
  
  Summarize the information:
  $$P=\answer{3460},\quad r=\answer{0.0035}$$
  
  How much money will there be in the account after each given number of years?  Round your answers to two decimal places.
  \begin{center}
\begin{tabular}{|c|c|}
 \hline
 &   \\
Number of years &  Amount \\
 &  \\
  \hline
  &  \\
 $1$ & $\answer{3472.13}$ \\
  & \\
 \hline
 &  \\
 $2$ & $\answer{3484.30}$ \\
  & \\
 \hline
 &  \\
 $10$ & $\answer{3583.24}$ \\
  & \\
 \hline
   \end{tabular}
\end{center}    
Sketch the graph to determine how long it will take for the amount to grow to  $\$5000$.  Use Desmos and round your answers to three decimal places.
  
  \begin{center}  
\desmos{vnpejaj7ps}{800}{600}  
\end{center}

It will take $\answer{105.191}$ years for the amount in the account to grow to $\$5000$.  
  \end{problem}
  
\section{Lecture 18}

\begin{problem}\label{prob:160hom7prob7}
Evaluate each exponential expression WITHOUT the use of a calculator.  
\begin{enumerate}
    \item $$25^{\frac{1}{2}}=\answer{5}$$
    \item $$0.01^{0.5}=\answer{0.1}$$
    \item $$3^{-2}=\answer{1/9}$$
    \item $$\left(\frac{1}{2}\right)^{-3}=\answer{8}$$
    \item $$32^{\frac{2}{5}}=\answer{4}$$
    \item $$\left(\frac{4}{9}\right)^{-\frac{3}{2}}=\answer{27/8}$$
\end{enumerate}
\end{problem}

\begin{problem}\label{prob:160hom7prob8}
Complete the statement.
 \begin{enumerate}
     \item 
 $\log_b a=p$ means $\answer{b^p}=\answer{a}$
 \item
 $\log x=q$ means $\answer{10^q}=\answer{x}$
 \item
 $\ln w=r$ means $\answer{e^r}=\answer{w}$
 \end{enumerate}
 \end{problem}
 
 \begin{problem}\label{prob:160hom7prob9}
 Evaluate each logarithmic expression WITHOUT the use of a calculator.
 \begin{enumerate}
     \item $$\log 10000=\answer{4}$$
     \item $$\log_4\frac{1}{16}=\answer{-2}$$
     \item $$\ln\sqrt{e}=\answer{1/2}$$
     \item $$\log_4 64=\answer{3}$$
     \item $$\log_4 32=\answer{5/2}$$
 \end{enumerate}
 \end{problem}
 
 \end{document}