\documentclass{ximera}

\author{Anna Davis} \title{MTH 160 Homework 7} 

\begin{document}

\begin{abstract}

\end{abstract}
\maketitle
 \textit{Certificate due: 10/28/2020 at 11:59 p.m.}
 \section{Lecture 20}
 
  \begin{problem}\label{prob:160hom8prob1} 
Use properties of logarithms to simplify without the use of a calculator.
\begin{enumerate}
    \item $e^{3\ln x}=\answer{x^3}$
    \item $\ln\left(\ln e^2\right)=\ln\answer{2}$
    \item $\log 2 +\log 50=\log \answer{100}=\answer{2}$
\end{enumerate}
\end{problem}

\begin{problem}\label{prob:160hom8prob8}
 Simplify as much as possible.
 \begin{enumerate}
     \item $\log_b \frac{1}{b}=\answer{-1}$
     \item $2\log 2+\log\frac{1}{4}=\answer{0}$
     \item $10^{\log a}=\answer{a}$
     \item $\ln\left(\log_b b\right)=\answer{0}$
 \end{enumerate}
 \end{problem}

\begin{problem}\label{prob:160hom8prob2}
Use change of base formula to evaluate. 

$$\log_3 12=\frac{\log\answer{12}}{\log\answer{3}}=\answer[tolerance=0.01]{2.26}$$
\end{problem}

\begin{problem}\label{prob:160hom8prob3}
Write the expression as a single logarithm.
$$\log x-3\log y+\frac{1}{2}\log z=\log\left(\frac{\answer{x\sqrt{z}}}{\answer{y^3}}\right)$$
\end{problem}

\begin{problem}\label{prob:160hom8prob10}
 Write as a single logarithm.
 
 $$\frac{1}{2}\log m+4\log n+5\log p=\answer{\log(\sqrt{m}n^4p^5)}$$
 \end{problem}
 
 \begin{problem}\label{prob:160hom8prob11}
 Write as a sum/difference of logarithms.
 
 $$\ln \frac{\sqrt{z}}{b^2}=\answer{0.5\ln z-2\ln b}$$
 \end{problem}

 \section{Lecture 21}
 
 \begin{problem}\label{prob:160hom8prob4}
Follow the indicated steps to solve for $x$.
$$300=150(1.12)^{24x}$$
Divide both sides by 150.
$$\answer{2}=1.12^{24x}$$
Take the natural log of both sides and bring the exponent to the front.
$$\answer[tolerance=0.01]{0.693}=\answer{24x}\ln\answer{1.12}$$
$$x=\answer[tolerance=0.01]{0.255}$$
\end{problem}

\begin{problem}\label{prob:160hom8prob5}
Solve for $x$.
$$3^{x-1}=9^{2-x}$$
$$x=\answer[tolerance=0.01]{\frac{5}{3}}$$
\end{problem}

\begin{problem}\label{prob:160hom8prob6}
Follow the indicated steps to solve for $x$.
$$\log (2x+3)=-1$$
Rewrite as an exponential expression.
$$10^{\answer{-1}}=\answer{2x+3}$$
$$x=\answer{-1.45}$$
\end{problem}

\begin{problem}\label{prob:160hom8prob7}
Solve for $x$.
$$450=700e^{-0.27x}$$
$$x=\answer[tolerance=0.01]{1.636}$$
\end{problem}

\begin{problem}\label{prob:160hom8prob9}
 Solve each equation for $x$.
 \begin{enumerate}
     \item $$16^{x-1}=2^x$$
     $$x=\answer[tolerance=0.03]{\frac{4}{3}}$$
     \item 
     $$100e^{3x}=120$$
     $$x=\answer[tolerance=0.001]{0.06}$$
     \item 
     $$10\log (2x)=20$$
     $$x=\answer{50}$$
 \end{enumerate}
 \end{problem}
 \end{document}