\documentclass{ximera}

\author{Anna Davis} \title{MTH 140 Homework 3} 

\begin{document}

\begin{abstract}

\end{abstract}
\maketitle
 \textit{Certificate due: 9/8/2020 at 11:59 p.m.}
\begin{problem}\label{prob:140hom3prob1}

Use the table below to compute sample standard deviation ($s$), for the following SAMPLE of test scores:
$$68, 73, 75, 81, 94$$

$$n=\answer{5}$$
$$\overline{x}=\answer{78.2}$$
Enter EXACT values into the table; no rounding.
\begin{center}
\begin{tabular}{|c|c|c|}
Test Scores & Deviations & Deviations Squared  \\
 \hline
 \hline
   & &\\
 68 &$\answer{-10.2}$  & $\answer{104.04}$ \\
  & &\\
  \hline
   & &\\
 73 &$\answer{-5.2}$  & $\answer{27.04}$\\
  & &\\
 \hline
  & &\\
 75 &$\answer{-3.2}$ &$\answer{10.24}$ \\
  & &\\
 \hline
  & &\\
 81 &$\answer{2.8}$  &$\answer{7.84}$ \\
  & &\\
 \hline
  & &\\
 94 &$\answer{15.8}$  &$\answer{249.64}$ \\
  & &\\
 \hline
  
\end{tabular}
\end{center}

$$s =\sqrt{\frac{\sum (x-\overline{x})^2}{n-1}}=\answer[tolerance=0.1]{10}$$
 \end{problem}


\begin{problem}\label{prob:140hom3prob2}
There are four gas stations in a small town.  One day in July, the gas prices were as follows:
$$1.94, 1.94, 1.99, 2.01$$
Fill out the table below to find the population standard deviation ($\sigma$).
$$N=\answer{4}$$
$$\mu=\answer{1.97}$$
Enter EXACT values into the table; no rounding.
\begin{center}
\begin{tabular}{|c|c|c|}
Price per Gallon & Deviations & Deviations Squared  \\
 \hline
 \hline
   & &\\
 1.94 &$\answer{-0.03}$  & $\answer{0.0009}$ \\
  & &\\
  \hline
   & &\\
 1.94 &$\answer{-0.03}$  & $\answer{0.0009}$\\
  & &\\
 \hline
  & &\\
 1.99 &$\answer{0.02}$ &$\answer{0.0004}$ \\
  & &\\
 \hline
  & &\\
 2.01 &$\answer{0.04}$  &$\answer{0.0016}$ \\
  & &\\
 \hline
 
\end{tabular}
\end{center}
Round $\sigma$ to four decimal places.
$$\sigma =\sqrt{\frac{\sum (x-\mu)^2}{N}}=\answer[tolerance=0.0001]{0.0308}$$
\end{problem}

\begin{problem}\label{prob:140hom3prob5}
Find the z-score for each of the test scores listed below.
\begin{enumerate}
    \item Cara's biology test score is 89.  The class average was 62 with standard deviation of 9.3.
    $$\mbox{Cara's z-score }=\answer[tolerance=0.01]{2.9}$$
    \item Zach's history test score is 68.  The class average is 76 with standard deviation of 5.2.
    $$\mbox{Zach's z-score }=\answer[tolerance=0.01]{-1.54}$$
    \item Ida's psychology test score is 92.  The class average was 81 with standard deviation of 10.2.
    $$\mbox{Ida's z-score }=\answer[tolerance=0.01]{1.08}$$
    
\end{enumerate}
\end{problem}

\begin{problem}\label{prob:140hom3prob3}
According to the College Board report for 2019, the mean SAT score was 1059 with standard deviation of 210.  During the 2017-18 testing year, the mean ACT score was 20.9 with standard deviation of 5.6.  

Suppose Maya scored 23 on her ACT.  A year later, Maya took the SAT and scored 1280.  Find Maya's z-score for each test.  Did she perform better on the ACT or the SAT?

Round z-scores to three decimal places.
$$\mbox{z-score for the ACT }=\answer{0.375}$$
$$\mbox{z-score for the SAT }=\answer[tolerance=0.001]{1.052}$$

\begin{multipleChoice}  
\choice{Maya scored better on the ACT}  
\choice[correct]{Maya scored better on the SAT}  
\choice{Maya's performance was about the same on both tests.}  
\end{multipleChoice}
\end{problem}

\begin{problem}\label{prob:140hom3prob4}

Alice (A), Ben (B), Catherine (C) and Doug (D) took the same biology test.  Assume that the scores on the test were normally distributed.  The results are listed below: 

Alice's score is in the $90$th percentile 

Ben's $z$-score is $z = 2$ 

Catherine's score is in the $10$th percentile 

Doug's $z$-score is $z = 0$

Arrange students’ initials (A, B, C and D) in order of increasing test results (lowest test result to highest test result).  Enter your answer as a single string, all capitals, no spaces.  e.g. ABCD.
$$\answer[format=string]{CDAB}$$
\end{problem}
\end{document} 


