\documentclass{ximera}

\author{Anna Davis} \title{MTH 140 Homework 4} 

\begin{document}

\begin{abstract}

\end{abstract}
\maketitle
 \textit{Certificate due: 2/8/2021 at 11:59 p.m.}

\begin{problem}\label{prob:140hom3prob5}
Find the z-score for each of the test scores listed below.
\begin{enumerate}
    \item Cara's biology test score is 89.  The class average was 62 with standard deviation of 9.3.
    $$\mbox{Cara's z-score }=\answer[tolerance=0.01]{2.9}$$
    \item Zach's history test score is 68.  The class average is 76 with standard deviation of 5.2.
    $$\mbox{Zach's z-score }=\answer[tolerance=0.01]{-1.54}$$
    \item Ida's psychology test score is 92.  The class average was 81 with standard deviation of 10.2.
    $$\mbox{Ida's z-score }=\answer[tolerance=0.01]{1.08}$$
    
\end{enumerate}
\end{problem}

\begin{problem}\label{prob:140hom3prob3}
According to the College Board report for 2019, the mean SAT score was 1059 with standard deviation of 210.  During the 2017-18 testing year, the mean ACT score was 20.9 with standard deviation of 5.6.  

Suppose Maya scored 23 on her ACT.  A year later, Maya took the SAT and scored 1280.  Find Maya's z-score for each test.  Did she perform better on the ACT or the SAT?

Round z-scores to three decimal places.
$$\mbox{z-score for the ACT }=\answer{0.375}$$
$$\mbox{z-score for the SAT }=\answer[tolerance=0.001]{1.052}$$

\begin{multipleChoice}  
\choice{Maya scored better on the ACT}  
\choice[correct]{Maya scored better on the SAT}  
\choice{Maya's performance was about the same on both tests.}  
\end{multipleChoice}
\end{problem}

\begin{problem}\label{prob:140hom3prob4}

Alice (A), Ben (B), Catherine (C) and Doug (D) took the same biology test.  Assume that the scores on the test were normally distributed.  The results are listed below: 

Alice's score is in the $90$th percentile 

Ben's $z$-score is $z = 2$ 

Catherine's score is in the $10$th percentile 

Doug's $z$-score is $z = 0$

Arrange students’ initials (A, B, C and D) in order of increasing test results (lowest test result to highest test result).  Enter your answer as a single string, all capitals, no spaces.  e.g. ABCD.
$$\answer[format=string]{CDAB}$$
\end{problem}




\end{document}